---
title: "p8105_hw1_cd3591"
author: "Anny"
date: "2025-09-19"
output: github_document
---

# Problem 1

```{r}
# set up the packages needed
library("moderndive")
library("tidyverse")
```

```{r}
# set up the dataset needed
data("early_january_weather")

# quick look for the variables in the dataset
early_january_weather
```

**Short Description**
The early_january_weather dataset has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.
Its variables contain: `r paste(names(early_january_weather), collapse = ", ")`. 
In specific, times range from `r min(early_january_weather$time_hour)` to `r max(early_january_weather$time_hour)`.
The mean temperature over this time period is `r mean(early_january_weather$temp, na.rm = TRUE)`.

```{r}
# make a scatterplot of temp(y) vs time_hour(x)
temp_vs_time_plot = ggplot(early_january_weather,
                           aes(x = time_hour, y = temp, color = humid)) + 
  geom_point() +
  labs(x = "Time (hour)", y = "Temperature", color = "Humidity") 
temp_vs_time_plot
```

```{r}
# export the scatterplot
ggsave("temp_vs_time.png", plot = temp_vs_time_plot)
```