---
title: "p8105_hw1_cd3591"
author: "Anny"
date: "2025-09-19"
output: github_document
---

# Problem 1

```{r}
# set up the packages needed
library("moderndive")
library("tidyverse")
```

```{r}
# set up the dataset needed
data("early_january_weather")

# quick look for the variables in the dataset
early_january_weather
```

**Short Description**
The early_january_weather dataset has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.
Its variables contain: `r paste(names(early_january_weather), collapse = ", ")`. 
In specific, times range from `r min(early_january_weather$time_hour)` to `r max(early_january_weather$time_hour)`.
The mean temperature over this time period is `r mean(early_january_weather$temp, na.rm = TRUE)`.

```{r}
# make a scatterplot of temp(y) vs time_hour(x)
temp_vs_time_plot = ggplot(early_january_weather,
                           aes(x = time_hour, y = temp, color = humid)) + 
  geom_point() +
  labs(x = "Time (hour)", y = "Temperature", color = "Humidity") 
temp_vs_time_plot
```

```{r}
# export the scatterplot
ggsave("temp_vs_time.png", plot = temp_vs_time_plot)
```

# Problem 2

```{r}
set.seed(1122)

# build the data frame
x_numeric = rnorm(n = 10) # a random sample of size 10 from a standard normal distribution
x_logical = x_numeric > 0 # whether the elements of the sample are greater than 0
x_character = sample(letters, 10)
x_factor = factor(sample(c("small", "medium", "large"), 10, replace = TRUE),
                  levels = c("small","medium","large"))

X = data.frame(numeric = x_numeric,
               logical = x_logical,
               character = x_character,
               factor = x_factor)

# quick look for the X data frame
X
```